\documentclass[letterpaper]{book}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\usepackage[paperwidth=11in,paperheight=17in,margin=1.00in]{geometry}
%\usepackage[paperwidth=297mm,paperheight=420mm,margin=25mm]{geometry}
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{float}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{parskip}
\begin{document}
\begin{titlepage}
\begin{flushright}
\vspace*{\stretch{1}}
{\Huge \bfseries LATER \\ }
{\large for four voices}
%{\large for bass flute, bass clarinet, tuba doubling on piano, harp, soprano, and percussion \\}
%{\large \bfseries for bass flute, bass clarinet, tuba/piano, soprano, harp, percussion, and tape \\}
\par
\vspace{\stretch{1}}
%{\Large Date of composition: 06/09-08/09}
{\large Text: Wassily Kandinsky \\}
{\large Music: Mike Solomon \\}
%{\large 10'}
%{\large BMI Student Composer Awards}
\end{flushright}
\end{titlepage}
\thispagestyle{empty} 
\frontmatter
\clearpage
\vspace*{\stretch{1}}
\section*{LATER}
In the deep summit I know I will find you. Where smooth pricks. Where sharp doesn't cut. You hold the 
ring in your left hand. I hold the ring in my right hand. No one sees the chain. But these rings are the 
last links of the chain.\\\hfill\\
The beginning.\\
The end.\\
\begin{flushright}
Wassily Kandinsky
\end{flushright}
\vspace*{\stretch{3}}
\clearpage
\vspace*{\stretch{1}}
\section*{Notes}
The work should be sung \emph{non vibrato}.\par
All words in the \emph{non legato} passages should be enunciated to an extreme by using broad lip movements and moving through diphthongs evenly instead of adding the diphthong at the end of the note.  Think of the type of facial gestures one makes when one mimics an overdubbed movie.  This is how these passages, which constitute the majority of the work, should be sung.\par
In some cases, syllables of words are sung outside the context of the full word.  When this occurs, the full word is presented in parentheses over the note to indicate the correct pronunciation.\par
Any lyrics that appear in brackets represent the a portion of the previous syllable sung backwards.  Try to sing as close to a retrograde as possible of the previous syllable.\par
The singers, while singing the \emph{legato} passage beginning at the pickup to measure 33 and lasting until beat two of measure 37, should use stagger breathing to create the smoothest impression possible.\par
For the faster passages, complete and exact articulation of the text may (should) be sacrificed in order to stay at tempo.\par
Please note that measures 28 and 59 are split over the line break at their respective midpoints in order to prevent the layout from being to crammed.
\vspace*{\stretch{3}}
\end{document}